Density dependence

### 2020-09-15 R/density dependence.Rmd
change density to lagged density.

```{r data, echo=TRUE}
ha <- read_rds(here("analysis", "data", "derived_data", "ha_density.rds"))
ha
```

@@

Scale year

```{r}
ha_cf <- 
  ha_cf %>% 
  ungroup() %>% 
  mutate(year_post = year - min(year))
```

@@

Can remove plot ID.

```{r}
mnorm4 <- glmer(shts ~ log(shts_prev) * density_0_10 + (1|year_post),
               family = gaussian(link = "log"),
               data = ha_cf)
AICtab(mnorm3, mnorm4)
```

Keep plant ID as a random effect.

```{r}
mnorm5 <- glmer(shts ~ log(shts_prev) * density_0_10 + (1|ha_id_number),
               family = gaussian(link = "log"),
               data = ha_cf)
AICtab(mnorm3, mnorm4, mnorm5)
```

@@

```{r}
h <- augment(mnorm2) %>% 
  ggplot(aes(.resid)) +
  geom_histogram()

qq <- augment(mnorm2) %>% 
  ggplot(aes(sample = .resid)) +
  geom_qq() + geom_qq_line()

resid<- augment(mnorm2) %>% 
  ggplot(aes(x = .fitted, y = .resid)) + geom_point() 
h/(qq|resid)
```
I don't love this, but it is a better fit than a poisson distribution.

@@

- Density should be total shoot number
- Should actually be density in previous year
- ~~Shoots should be poisson distribution, not log-transformed?~~
- incorporate 1-ha fragments and use habitat type as a predictor.
- Implement FLM approach to density dependence.

>>>>

```{r data, echo=TRUE}
ha <- read_rds(here("analysis", "data", "derived_data", "ha_density.rds"))
ha
```
Actually interested in density in the previous year

```{r}
ha <-
  ha %>% 
  group_by(ha_id_number) %>% 
  arrange(ha_id_number, year) %>% 
  mutate(across(starts_with("density"), lag)) %>% 
  ungroup() %>% 
  #scale year
  mutate(year_post = year - min(year))
```

@@

@@

Can't remove plot ID.

```{r}
mnorm4 <- glmer(shts ~ log(shts_prev) * density_0_10 + (1|year_post) + (1|plot),
               family = gaussian(link = "log"),
               data = ha_cf)
AICtab(mnorm2, mnorm4)
```

Can't remove plant ID

```{r}
mnorm5 <- glmer(shts ~ log(shts_prev) * density_0_10 + (1|ha_id_number) + (1|plot),
               family = gaussian(link = "log"),
               data = ha_cf)
AICtab(mnorm2, mnorm3, mnorm4, mnorm5)
```

@@

```{r}
ha_aug <- augment(mnorm2)
h <-
  ggplot(ha_aug, aes(.resid)) +
  geom_histogram()

qq <-
  ggplot(ha_aug, aes(sample = .resid)) +
  geom_qq() + geom_qq_line()

resid<- 
  ggplot(ha_aug, aes(x = .fitted, y = .resid)) + geom_point() 
h/(qq|resid)
```
I don't love this, but it is a better fit than a poisson distribution.

@@

- ~~Density should be total shoot number~~
- ~~Should actually be density in previous year~~
- ~~Shoots should be poisson distribution, not log-transformed?~~
- incorporate 1-ha fragments and use habitat type as a predictor.
- Implement FLM approach to density dependence.
